\section{Spectroscopy vs. Crystallography}
	
\textbf{Spectroscopy} is the study of absorption and/or emission of electromagnetic radiation in which the incident radiation interacts with the molecule and produces characteristic signals. From spectroscopy, we can get the following data about a molecule:%
%			
\begin{itemize}%
%		
    \item Bond lengths and bond angles of simple (diatomic, triatomic) molecules.
    
    \item Combination of Infrared and NMR (${}^1 \mathrm{H}$ and ${}^{13} \mathrm{C}$) spectroscopy provides information about functional groups, bond connectivity and stereochemistry (absolute configuration) of simple molecules.
    
    \end{itemize}
    
Spectroscopy, however, cannot provide information about bond lengths, bond angles, torsion angles, etc.\ of complicated molecules.

\textbf{Crystallography}, on the other hand, deals in the interaction of EM radiation of very small wavelength ($\lambda \sim \SI{1}{\angstrom}$) with solid materials (crystalline or amorphous) through scattering. The main difference with spectroscopy is that in crystallography, there is no absorption or emission of radiation; only scattering of radiation. Crystallography allows us to study%
%			
\begin{itemize}%
%			
    \item Accurate bond length, bond angles, torsion angles, precise absolute configuration, etc.\ of all types of crystalline substances.
    
    \item 3D structure of crystalline substances can lead to intermolecular or inter-ionic interactions. Structure property relationship can be obtained using data from crystallography.
    
\end{itemize}